Toxic Code Snippets on Stack Overflow

### 2018-11-24 cloverflow-tse/cloverflow.tex
Injected some (self) citations. Updated the bios.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, emse, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2)~\cite{Bellon2007}. \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. He was supervised by Dr.~Jens Krinke and Dr.~David Clark. His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repository. More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
\end{IEEEbiography}
\vspace{-1cm}

% % if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
is Senior Lecturer in the Software Systems Engineering
Group at the University College London, where he is Director of CREST,
the Centre for Research on Evolution, Search, and Testing.  His main
focus is software analysis for software engineering purposes. His
current research interests include software
similarity, modern code review, and mutation testing.  He is well known for his work on
program slicing and clone detection.
\end{IEEEbiography}
\vspace{-1cm}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
is currently a PhD candidate in the Computer Science Department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
\end{IEEEbiography}
\vspace{-1cm}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{giuseppe.png}}]{Giuseppe Bianco}
  received his bachelor degree in Computer Science from the University
  of Molise (Italy) under the supervision of Dr.~Rocco Oliveto. As
  part of an Erasmus+ traineeship, he spent three month at the
  CREST centre, University College London, UK, under the supervision
  of Dr.~Jens Krinke.~He is now a project manager at Corsi.it.
\end{IEEEbiography}
\vspace{-0.5cm}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rocco.png}}]{Rocco Oliveto}
is Associate Professor at University of Molise (Italy), where he is also the Director of the Computer Science Bachelor and Master programs and the Director of the Software and Knowledge Engineering Lab (STAKE Lab). He co-authored over 100 papers on topics related to software traceability, software maintenance and evolution, search-based software engineering, and empirical software engineering. His activities span various international software engineering research communities. He has served as organizing and program committee member of several international conferences in the field of software engineering. He was program co-chair of ICPC 2015, TEFSE 2009 and 2015, SCAM 2014, WCRE 2012, and 2013. He is general chair for SANER 2018 that will be held in Campobasso from March 20, 2018 to March 23, 2018. He is also one of the co-founders and CEO of DataSound, a spin-off of the University of Molise aiming at efficiently exploiting the priceless heritage that can be extracted from big data analysis via machine learning. 
More info at \url{https://dibt.unimol.it/staff/oliveto}.
\end{IEEEbiography}
\vfill

>>>>

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, emse, Wang2013, Mondal2011, Cheung2015,
  krinke11cloned, Krinke2010, krinke10distinguishing, Krinke2008,
  krinke07study, ragkhitwetsagul18picture}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2)~\cite{Bellon2007}. \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repositories. More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
\end{IEEEbiography}
%\vspace{-1cm}

% % if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
is Associate Professor in the Software Systems Engineering
Group at the University College London, where he is Director of CREST,
the Centre for Research on Evolution, Search, and Testing.  His main
focus is software analysis for software engineering purposes. His
current research interests include software
similarity, modern code review, program analysis, and software testing.  He is well known for his work on
program slicing and clone detection.
\end{IEEEbiography}
%\vspace{-1cm}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
is currently a PhD candidate in the Computer Science Department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
\end{IEEEbiography}
%\vspace{-1cm}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{giuseppe.png}}]{Giuseppe Bianco}
  received his bachelor degree in Computer Science from the University
  of Molise (Italy) under the supervision of Dr.~Rocco Oliveto. As
  part of an Erasmus+ traineeship, he spent three month at the
  CREST centre, University College London, UK, under the supervision
  of Dr.~Jens Krinke.~He is now a project manager at Corsi.it.
\end{IEEEbiography}
%\vspace{-0.5cm}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rocco.png}}]{Rocco Oliveto}
is Associate Professor at University of Molise (Italy), where he is
also the Director of the Computer Science Bachelor and Master programs
and the Director of the Software and Knowledge Engineering Lab (STAKE
Lab).
He is also one of the co-founders and CEO of DataSound, a spin-off of the University of Molise aiming at efficiently exploiting the priceless heritage that can be extracted from big data analysis via machine learning. 
\end{IEEEbiography}
\vfill
